Modelling last glacial cycle ice dynamics in the Alps

### 2017-08-08 articles/cycle/alps-cycle.tex
Add Rhine scaling domain on footprints figure.
Move map below scatter plot on trimline figure.
Fix Isère label on profile plot.
Tried plotting several contours for ice thickness but that is too much info.

    \begin{figure}
      \centerline{\includegraphics{alpcyc_lr_footprints}}
      \caption{%
        \textbf{(a--c)} Cumulative extent of modelled ice cover during MIS~2
        (29--14\,ka), with (light colours) and without (dark colours)
        palaeo-precipitation corrections, and using temperature time-series
        scaling factors (Table~\ref{tab:records}) adjusted to model the area
        glaciated by the Rhine glacier piedmont lobe (black rectangle) in
        agreement with the Last Glacial Maximum (LGM) geomorphological
        reconstruction \citep[solid red line,][]{Ehlers.etal.2011}.
        \textbf{(d--f)} Cumulative extent of modelled ice cover during MIS~4
        (71--57\,ka). Only the simulation driven by the EPICA temperature
        time-series yields reasonable MIS~4 ice cover.
        \todo{Add Rhine lobe scaling domain.}}
      \label{fig:footprints}
    \end{figure}

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{%
        \textbf{(a)} Modelled age of maximum ice thickness (colour) and maximum
        ice surface elevation (200\,m contours) above trimline locations
        \citep[Table~1]{Kelly.etal.2004} in the upper Rhone valley.
        \textbf{(b)} Modelled maximum ice thickness against observed trimline
        elevations \citep[Table~1]{Kelly.etal.2004}.
        \textbf{(c)} Histogram of modelled maximum ice thickness above trimline
        locations (500\,m bands). The average maximum ice thickness above the
        trimline is 979\,m.
        \todo{Move map below scatter plot and add cold ice areas or so. Use max
              surface elevation age as in Fig.~\ref{fig:timing}.}}
      \label{fig:trimlines}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{%
        Modelled glacier extent and thickess along selected profiles for the
        Rhine, Rhone, Ivrea and Isère glaciers.
        \todo{Add accent on Isère, show ice thickness.}}
      \label{fig:profiles}
    \end{figure}

>>>>

    \begin{figure}
      \centerline{\includegraphics{alpcyc_lr_footprints}}
      \caption{%
        \textbf{(a--c)} Cumulative extent of modelled ice cover during MIS~2
        (29--14\,ka), with (light colours) and without (dark colours)
        palaeo-precipitation corrections, and using temperature time-series
        scaling factors (Table~\ref{tab:records}) adjusted to model the area
        glaciated by the Rhine glacier piedmont lobe (black rectangle) in
        agreement with the Last Glacial Maximum (LGM) geomorphological
        reconstruction \citep[solid red line,][]{Ehlers.etal.2011}.
        \textbf{(d--f)} Cumulative extent of modelled ice cover during MIS~4
        (71--57\,ka). Only the simulation driven by the EPICA temperature
        time-series yields reasonable MIS~4 ice cover.}
      \label{fig:footprints}
    \end{figure}

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{%
        \textbf{(a)} Modelled age of maximum ice thickness (colour) and maximum
        ice surface elevation (200\,m contours) above trimline locations
        \citep[Table~1]{Kelly.etal.2004} in the upper Rhone valley.
        \textbf{(b)} Modelled maximum ice thickness against observed trimline
        elevations \citep[Table~1]{Kelly.etal.2004}.
        \textbf{(c)} Histogram of modelled maximum ice thickness above trimline
        locations (500\,m bands). The average maximum ice thickness above the
        trimline is 979\,m.
        \todo{Add cold ice areas or so. Use max
              surface elevation age as in Fig.~\ref{fig:timing}.}}
      \label{fig:trimlines}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{%
        Modelled glacier extent and thickess along selected profiles for the
        Rhine, Rhone, Ivrea and Isère glaciers.}
      \label{fig:profiles}
    \end{figure}
